\documentclass[11pt,english]{article}

\usepackage{babel}
\parskip 1em

\begin{document}

\makebox[\textwidth]{\huge \textbf{Opponent Report}}

\vspace{10pt}

\makebox[\textwidth]{\large \textit{Dept. of Computer Science \& Engineering, RUET}}
\\
\vspace{10pt}
{--------------------------------------------------------------------------------------------------}\\\\
{\large \textbf{Author of thesis: }}Shubho Kumar Das \& Md. Ali Ashraf\\\\
{\large \textbf{Thesis title: }}COMPARISON BETWEEN BELLMAN FORD AND DIJKSTRA ALGORITHM IN GIS SYSTEM\\\\
{\large \textbf{Opponent: }}Mir Mursalin Ankur\\\\
\\\\\\
{\large \textbf{1. To what extent does the thesis title reflect the content of the report?}}\\\\
The thesis title reflects much of  report.\\\\
{\large \textbf{2. How does the author describe the problem background?}}\\\\
It is mostly understandable for the reader who have basic idea of graph representation in computer science but not much satisfactory for a general reader.\\\\
{\large \textbf{3. Has the author presented the results clearly?}}\\\\
Yes.\\\\
{\large \textbf{4. Do you find the author\textsc{\char39}s conclusions credible?}}\\\\
Yes.\\\\
{\large \textbf{5. Does the literature (References) seem relevant?}}\\\\
Some irrelevant references were seen in the paper. Such as -\\
  \\i. Reference [4] was not used in paper.\vspace{5pt}
  \\ii. Reference [7] isn\textsc{\char39}t relevant to paper.\vspace{5pt}
  \\iii. Reference [9] mentioned of a website which doesn't give direct access to relevant topic.\vspace{5pt}
  \\iv. There is nothing named igragh viewed in reference [11].\vspace{5pt}
  \\v. References [8] and [13] mentioned same web link which do not have any of the title referred.\\\\
{\large \textbf{6. Which are the strengths and weaknesses of the report?}}\\\\
The paper is mostly understandable but there are some gaudy imperfection. Such as -\\
  \\i. Punctuation marks were not used correctly so it is tough to understand alongside sentences which is remarkable from abstract.\vspace{5pt}
  \\ii. Algorithm shown in the paper is not vision comfortable.\vspace{5pt}
  \\iii. Negative cycle is a key fact in comparison between both algorithm according to paper. But there is no definition of negative cycle.\vspace{5pt}
  \\iv. Introduction should be more detailed.\\\\
{\large \textbf{7. Is the report plagiarism free?}}\\\\
Yes. Plagiarism is below 30\%.\\\\
{\large \textbf{8. Questions to the author(s) (If any) [Optional]:}}\\\\
None.\\\\
\end{document} 